Comparison of FDR methods on GWAS with SummarizedBenchmark

### 2017-12-22 datasets/GWAS/GWAS-SummarizedBenchmark.Rmd
restrict max number of methods in boxplot to 3

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
mcols(sb)$ind_covariate <- mcols(sb)$ind_covar_N
plotCovariateBoxplots(sb, alpha=0.1, nsets=6, methods=methods, trans=log2, maxNum=5)

@@

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
mcols(sb)$ind_covariate <- abs(mcols(sb)$ind_covar_AF-0.5)
plotCovariateBoxplots(sb, alpha=0.1, nsets=6, methods=methods, maxNum=5)

>>>>

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf",
             "scott-empirical", "scott-theoretical")
mcols(sb)$ind_covariate <- mcols(sb)$ind_covar_N
plotCovariateBoxplots(sb, alpha=0.1, nsets=6, methods=methods, trans=log2, maxNum=3)

@@

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf",
             "scott-empirical", "scott-theoretical")
mcols(sb)$ind_covariate <- abs(mcols(sb)$ind_covar_AF-0.5)
plotCovariateBoxplots(sb, alpha=0.1, nsets=6, methods=methods, maxNum=3)
